Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/impl.tex
discuss experimental results

>>>>

\subsection{Implementation of the Correlated-Calls Analysis}

We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
Our implementation analyzes JVM bytecode compiled from input programs written
in Java.
%
We use WALA~\cite{fink2012wala} to retrieve information about an input program, such 
as its control-flow supergraph and the set of receivers and their types.
Since WALA does not contain an implementation of the IDE algorithm,
we implemented it from scratch.
We will submit our implementation to the artifact evaluation committee, and are also 
working on contributing our infrastructure to WALA.

We tested our correlated-calls analysis using an IFDS taint-analysis  
as a client analysis. To this end, we converted the IFDS taint analysis into an IDE problem with an 
implementation of $\transCC_\rcc$. We extensively tested the correlated-calls analysis to ensure that, in 
the absence of correlated calls, the analysis produces the same results as an IFDS-equivalent analysis, and that 
it produces more precise results in the presence of correlated calls as expected.

To evaluate the practicality of our work, we applied two variants of the IFDS taint analysis
to the SPEC JVM98 benchmarks: (i) an equivalent IDE taint analysis obtained using $\transEq$, and (ii)
an IDE taint analysis obtained using   $\transCC_\rcc$ that avoids imprecision due to correlated method
calls. Unfortunately, for the specific combination of this IFDS client analysis and these benchmark
programs, the precise tracking of data flow in the presence of correlated calls does not impact precision. 
However, the good news is that the running times of the two analyses are roughly the same, ranging from 
a few seconds on the smaller SPEC programs to about two hours on \texttt{javac} in each cases (see the Appendix
for more details on these results).  This suggests that the overhead of tracking correlated calls is manageable,
and that our technique may be worthwhile in other scenarios.

\commentout{
The artifact of our implementation can be used to solve any IFDS problem. In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
}
